---
title: "rROMADash"
author: '[Luca Albergante](mailto:luca.albergante@gmail.com)'
date: "May 2017"
output:
  md_document:
    toc: yes
    toc_depth: 2
  html_document:
    depth: 3
    keep_md: yes
    number_sections: yes
    toc: yes
---

This package provides a shiny interface that can be used to complement the [rRoma R package](https://github.com/Albluca/rRoma).

# Intalling rROMADash

The rROMADash package relies on the `rRoma` package, which needs to be installed via `devtools`

```{r, eval=FALSE}
if(!requireNamespace("devtools")){
  install.packages("devtools")
}
devtools::install_github("Albluca/rRoma")
```

After installing `rRoma`, it is possible to install `rROMADash` by typing

```{r, eval=FALSE}
if(!requireNamespace("devtools")){
  install.packages("devtools")
}
devtools::install_github("Albluca/rRomaDash")
```


The other packages required by the interface will be installed automatically by R if not already available on the system.

# Using rROMADash

To launch the interface it is sufficient to type to following command:

```{r, eval=FALSE}
library(rRomaDash)
rRomaDash()
```

It is also possible to enable interactivity (via the `plotly` package), by typing

```{r, eval=FALSE}
library(rRomaDash)
rRomaDash(Interactive = TRUE)
```

Note that the interactivity is still experimental and may not work properly on certain systems.

# Using the docker container

A docker image containing the RStusio web server and all the necessary packages needed to run rRoma and rRomaDash is also available. After installing [docker](http://www.docker.com), the image can be obtained using 

```{r, engine='bash', eval=FALSE}
docker pull albluca/rroma
```

After installation, the image can be started with the command

```{r, engine='bash', eval=FALSE}
docker run -p 8787:8787 albluca/rroma
```

At this point, the RStudio web interface will be availabe. In Unix-like systems, the interface will be available at the address http://localhost:8787. It is then possible to access the interface by using "rstudio" as the username and password.

On windows, it may be necessary to replace localhost with the address of the machine. If any problem is encountered see the instruction [here](https://github.com/rocker-org/rocker/wiki/Using-the-RStudio-image).

After starting the interface, it is possible to write r code as in the desktop version of RStudio.
