---
title: "rROMADash"
author: '[Luca Albergante](mailto:luca.albergante@gmail.com)'
date: "May 2017"
output:
  md_document:
    toc: yes
    toc_depth: 2
  html_document:
    depth: 3
    keep_md: yes
    number_sections: yes
    toc: yes
---

This package provides a shiny interface that can be used to complement the [rRoma R package](https://github.com/Albluca/rRoma).

# Intalling rROMADash

The rROMADash package relies on the `rRoma` package, which needs to be installed via `devtools`

```{r, eval=FALSE}
if(!requireNamespace("devtools")){
  install.packages("devtools")
}
devtools::install_github("Albluca/rROMA")
```

The other packages required by the interface will be installed automatically by R if not already available on the system.

# Using rROMADash

To launch the interface it is sufficient to type to following command:

```{r, eval=FALSE}
library(rRomaDash)
rRomaDash()
```

It is also possible to enable interactivity (via the `plotly` package), by typing

```{r, eval=FALSE}
library(rRomaDash)
rRomaDash(Interactive = TRUE)
```

Note that the interactivity is still experimental and may not work properly on certain systems.

